Multiple linear regression

### 2018-11-27 DATA606/Lab8/michael-multiple_regression.Rmd
More work

    **Academia attracts people with below average beauty.  The median beauty score on a scale of 1 to 10 is a 4.  Males are less attractive than females.**

@@

@@

    **Nearly normal residuals: The plot below shows the Q to Q plot but it doesn't hold to the line the best.**

@@

```{r scatter-score-bty_avg_gender, eval = FALSE}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
summary(m_bty_gen)
```

@@

8.  Is `bty_avg` still a significant predictor of `score`? Has the addition
    of `gender` to the model changed the parameter estimate for `bty_avg`?

@@

@@

>>>>

    **The median beauty score is a 4 on a scale of 1 to 10.  Males are less attractive than females.**

@@

    **Nearly normal residuals: The plot abovew shows the Q to Q plot which is mostly normal, but the skew in the data is apparent in the figure.**

@@

    **Constant variability: The preceeding plot shows no apparent pattern in the residuals.**

@@

```{r scatter-score-bty_avg_gender}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
summary(m_bty_gen)
```

@@

    ```{r}
    plot(m_bty_gen$residuals ~ evals$bty_avg)
    abline(h = 0, lty = 3)
    ```

    **The residuals have a constant variability.**

    ```{r}
    qqnorm(m_bty_gen$residuals)
    qqline(m_bty_gen$residuals) 
    ```

    **The Q-Q plot is more linear than the previous one.**

8.  Is `bty_avg` still a significant predictor of `score`? **The predictor is statistically significant.** Has the addition of `gender` to the model changed the parameter estimate for `bty_avg`? **Yes.  It is now 0.07416 up from 0.06664.**

@@

    **All esle equal the male professor would have a higher course evaluation score.**

@@

    ```{r}
    m_bty_rank <- lm(score ~ bty_avg + rank, data = evals)
    summary(m_bty_rank)
    ```
